### 2015-11-06 CVPR16/Source/experiments2.tex
changes

\vspace{-0.4cm}
\paragraph{Setup}

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we create organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
    %$\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
    % \EnergyBBox+\EnergyDyn+\EnergyCol $
    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
  \label{tab:localizationExperiment}
\end{table}

>>>>

\vspace{-0.2cm}
\paragraph{Setup}

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we create organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

@@

%  seqName   seqNum    Energy_description                                                    windows         t      yaw             dim        
%    City      1       contPtTracksNoOcc_ctBBoxNoOcc_size_posTmcmc_inference      9/18  5.811142 0.696358        1.961227        
%    City      1       contPtTracksNoOcc_contBBoxOcc_size_posTmcmc_inference      8/18  4.501543 0.786599        2.375481        
%    City      1       contPtTracks_ctBBoxNoOcc_size_posTmcmc_inference           8/18  3.932855 0.766397        2.222919        
%    City      1       contPtTracks_contBBoxOcc_size_posTmcmc_inference           8/18  4.928155 0.806356        2.287911        
% OccCity      1       contPtTracksNoOcc_ctBBoxNoOcc_size_posTmcmc_inference      9/18  3.953464 0.442196        1.720844        
% OccCity      1       contPtTracksNoOcc_contBBoxOcc_size_posTmcmc_inference      8/18  4.815849 0.463034        2.159956        
% OccCity      1       contPtTracks_ctBBoxNoOcc_size_posTmcmc_inference           8/18  4.058560 0.995495        1.593641        
% OccCity      1       contPtTracks_contBBoxOcc_size_posTmcmc_inference           8/18  3.241853 0.631901        2.167446        
\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
    %$\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
    % \EnergyBBox+\EnergyDyn+\EnergyCol $
    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
  \label{tab:localizationExperiment}
\end{table}
